---
title: "Accessing Twitter Data"
author: "Zachary Steinert-Threlkeld"
institute: "Luskin School of Public Affairs, UCLA"
date: "09.08.2020"
output: 
  beamer_presentation:
    theme: "Warsaw"
    colortheme: "beaver"
    fonttheme: "structurebold"
    keep_tex: true
    toc: true
    includes:
      in_header: /Users/Zack/Documents/UCLA/Template/beamer_header.txt

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction
## Me + Twitter + Research
\begin{block}{Geolocated tweets to understand protests}
\begin{itemize}
\item Streaming API for tweets in real time, multiple connections (apps) for multiple tasks.
\item REST API for follower, friend relationships.
\item REST API for tweet history.
\end{itemize}
\end{block}

## !(Me + Twitter + Research)
\begin{itemize}
\item Search API
\item Experiments (bots)
\end{itemize}
\vspace{1cm}
\pause
\emph{As of July 2020, \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter is deploying a major update, v2, of its API}.  This course assumes v1, which is still the standard.}

## Self-Promotion
\begin{columns}[onlytextwidth,T]
  \begin{column}{.45\linewidth}
    \includegraphics[width=\linewidth]{../../Images/tad_cover.jpg}
  \end{column}
  \begin{column}{.45\linewidth}
  \emph{Twitter as Data}
    \begin{itemize}
    \item 2018, largely developed 2014-2016.
    \item R + Python. \pause
    \item Old: idiosyncratic technical features (rate limits, API endpoints), application creation was simpler.
    \item Today: Updated app creation; \texttt{rtweet}.
    \end{itemize}
    
  \end{column}
\end{columns}

## Pacing
If you want or need to create a Twitter developer account, please try to follow the steps as I present them.
- Do not hesitate to ask a question or ask me to slow down.

If you are not able to create an app in time for the next class, do not worry. \pause
- I expect you will not get the application for a developer account.
- \texttt{rtweet} lets you authenticate as a user, meaning you can work on your own Twitter code in the next lecture.

# Make Account

## Website
\centering
\includegraphics[width=\linewidth]{../../Images/twitter_newaccount.png}


## Create Account
\centering
\includegraphics[width=.9\linewidth]{../../Images/twitter_newaccount2.png}

## Create Account
\centering
\includegraphics[width=\linewidth]{../../Images/twitter_newaccount3.png}

## Developer Screen
\vspace{-.25cm}
\href{developer.twitter.com}{developer.twitter.com} \

\includegraphics[width=\linewidth]{../../Images/twitter_developer1.png}


## Apply for Developer Account
\vspace{-.25cm}
\href{https://developer.twitter.com/en/apply-for-access}{First time ever, apply for developer account.} \

\includegraphics[width=\linewidth]{../../Images/twitter_developer2.png}


## Apply for Developer Account
\vspace{-.25cm}
After many questions, you will see this screen.  \
\begin{center}
\includegraphics[width=.75\linewidth]{../../Images/twitter_developer3.png} \
\end{center}
\vspace{-.25cm}
Approval for a developer account takes a stochastic amount of days.



## Tips
\begin{itemize}
\item I prefer to have one account per e-mail address, separate browsers too if possible. \pause But with @gmail, add . within address and Google ignores the period but Twitter does not.
\item If developer-only account, use semi-regularly to not look like a bot.
\end{itemize}



# Create Application

## Apply
\vspace{-.25cm}
\href{https://developer.twitter.com/en/apps/}{https://developer.twitter.com/en/apps/} \
\includegraphics[width=\linewidth]{../../Images/twitter_devApp1.png}

## Apply
\vspace{-.25cm}
I prefer my account's Twitter homepage for the website URL. \
\centering
\includegraphics[height=.75\linewidth]{../../Images/twitter_devApp2.png}

## Apply
\vspace{-.25cm}
You \emph{must use} this callback URL for \texttt{rtweet}. \
NB: \texttt{rtweet} is the first time I have seen someone require the Callback URL.  No apps I have created otherwise have it, and they work fine.
\centering
\includegraphics[height=.75\linewidth]{../../Images/twitter_devApp3.png}

## Apply
\vspace{-.25cm}
The application is now available for use. \pause \emph{I am surprised it happened instantaneously.} \
\centering
\includegraphics[width=\linewidth]{../../Images/twitter_devApp4.png}

# Generate Token

## Overview
To use Twitter's API, you must create a token for the application.  The token is a trusted certificate that you will later present to Twitter each time you connect to an API endpoint. \

Two authentication methods.
\begin{enumerate}
\item Browser based from R
\item \emph{Access token \& access token secret}
\end{enumerate}

I prefer \#2, and it is what I show today.  Both enable the same functionality, but \#2 does not require an interactive session, which is important once you want to set up a persistent data collection pipeline.

## Navigate to App
\vspace{-.25cm}
\centering
\includegraphics[width=\linewidth]{../../Images/twitter_devApp4.png}

## Note Consumer API Keys
\centering
\includegraphics[width=\linewidth]{../../Images/twitter_authentication1.png}

## Note Consumer API Keys
```{r, eval=FALSE, echo=TRUE}
api_key <- 'CkUcfEdIvlX9c4OkBwcv062ay'
api_key_secret <- 'lS8AuQKK7g4SD6KWzFJ84qEW7Ewqcv2OJIt
NcwHJJWJYtumGfm'
```


## Generate Access Token
\centering
\includegraphics[width=\linewidth]{../../Images/twitter_authentication2.png}

## Use Keys and Token String
```{r, eval=FALSE, echo=TRUE}
api_key <- 'CkUcfEdIvlX9c4OkBwcv062ay'
api_key_secret <- 'lS8AuQKK7g4SD6KWzFJ84qEW7Ewqcv2OJI
tNcwHJJWJYtumGfm'
access_token <- '2K5LMiEwu2YXLK2389nslaqZoQA4Xc2uyI955
1451ZYIwaEmA94'
access_token_secret <- 'e5byw45zx7xc5d5EIPnEN1fasdf1mt
9vpi1fiFlZQpfbk2x62-w2kxKg'
```

## Create Token
```{r, eval=FALSE, echo=TRUE}
## install rtweet from CRAN
#install.packages("rtweet")

# load rtweet package
library(rtweet)

wildfire <- create_token(
  app = "Tracking_Hurricanes",
  consumer_key = api_key,
  consumer_secret = api_secret_key,
  access_token = access_token,
  access_secret = access_token_secret
  )
```
\texttt{wildfire} is now the object containing the token, and rtweet has stored it as an environment variable.  Future sessions will automatically load it.

## Tips
\begin{itemize}
\item Twitter is nice to academic research, so be honest.
\item Application approval process is opaque and often slow.  \pause Perhaps a current favoring of COVID-19 research.
\item Do not have apps duplicate work ``or substantially similar or overlapping use cases".
\end{itemize}

## Tips
\begin{itemize}
\item You may eventually have many apps and therefore many keys.  Keep a document that tracks them.  Do not share this document.
\end{itemize}

## My Key Tracking
\includegraphics[width=\linewidth]{../../Images/twitter_keyTracking.png}

## App vs. User Auth
- You will notice, especially when checking rate limits, a distinction between user and app authentication. \

- User authentication is for when a user gives your app permission to perform certain functions for it, and these functions have higher rate limits.  \href{https://developer.twitter.com/en/docs/authentication/oauth-1-0a/obtaining-user-access-tokens}{See the process here.} \

- Since my research, and creating event data more broadly, does not involve users of an application, I always use app authorization only.

## If Time
If we have reached this slide and time remains in the class, I will create a new application from scratch.
